Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-21 paper/Draft.tex
Stacking all IRF plots. Replicating Coibion close enough.

>>>>

In Figure \ref{ReplicateCoibionBefore2007}, I replicate the results from  \cite{coibion2012can}. The period is between 1987-2007.  In the right column, I do the same exercise with monetary policy shocks.

In Figure \ref{ReplicateCoibionpost2007}, I do the same exercise but include additional uncertainty. This is also the period when SPF provides density forecasts that allow me to estimate uncertainty.

\begin{figure}[h]\label{ReplicateCoibionBefore2007}
	\centering
	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_nmp.png}  
	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks.png} \\
	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_nmp.png} 
	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks.png}  \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp.png} 
		\includegraphics[width=6cm]{figures/SPFFE_ashocks.png} \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
		\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks.png} 
	\caption{ Replicating \cite{coibion2012can}: 1987-2007}
\end{figure}

\begin{figure}[h]\label{ReplicateCoibionpost2007}
	\centering
	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_nmp_post2007.png}  
	\includegraphics[width=6cm,height=2cm]{figures/CPIAU_ashocks_post2007.png} \\
	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm,height=2cm]{figures/PCEPI_ashocks_post2007.png}  \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm]{figures/SPFFE_ashocks_post2007.png} \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_post2007.png} \\
	\smallskip 
		\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_nmp_post2007.png} 
	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_post2007.png} 
	\caption{ Replicating \cite{coibion2012can}: 2008-2019}
\end{figure}
